Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-10-12 pkg/disttree/inst/draft/rejoinder.tex
some more revision based on reviews
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2324 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 70cc66cef334356c8f237acd0a6507e9902cb99b

We have adapted the introduction of a basic EMOS in the main manuscript
in Section~ ...
% By a `basic EMOS' we are referring to the linear distributional 
% regression model based on the idea presented by Gneiting et al. (2005) 
% where only the ensemble mean is included for the location parameter 
% and the ensemble standard deviation for the scale parameter.

@@

We used ``EMOS'' as an expression for a standard post-processing
model output statistics (MOS, Gneiting et al. (2005)) with a censored 
distribution. We have revised the introduction of the EMOS model in 
the main manuscript and hope this now explains the model better.

\textit{FIX ME: add formula for EMOS?}

\begin{reto}
Chen ist auf jeden Fall non-sense. Es gibt viele Papers die
sowas machen, die Frage ist, ob es 10 Referenzen braucht (unter
anderem macht das Jakob, Manu, ich, die Gneiting-Gruppe bzw.
Hamill-Gruppe hat auch was in die Richtung aber mit Gamma \dots).

Effizienter waere es wohl kurz das hier EMOS genannte Modell (was
eigentlich einfach ein non-homogeneous regression Modell ist)
im Appendix kurz hinzuschreiben?

    \begin{equation}
        \begin{split}
            y^{1/p} = \mathcal{N}_0(\mu, \sigma) \\
            \mu = \beta_0 + \beta_1 \cdot \bar{\mbox{tp}^{1/p}} + \mbox{split?} \\
            \log(\sigma) = \gamma_0 + \gamma_1 \cdot \mbox{sd}(\mbox{tp}^{1/p}) + \mbox{split?}
        \end{split}
    \end{equation}

\dots damit k\"onnte man auch auf Kommentar 8 von Reviewer 2 reagieren.
\end{reto}

>>>>

By a `basic EMOS' we are referring to the linear distributional 
regression model based on the idea presented by Gneiting et al. (2005) 
applying a left-censored at zero Gaussian distribution where only the 
ensemble mean is included for the location parameter and the ensemble 
standard deviation for the scale parameter.
We have introduced the model which we are referring to as a basic EMOS 
in detail in the main manuscript in the first paragraph of Section~3.

@@

We used ``EMOS'' as an expression for a standard post-processing
model output statistics (MOS, Gneiting et al. (2005)) with a censored 
distribution. We have revised the introduction of the EMOS model in 
the main manuscript in Section~3 and hope this now explains the model better.

\textit{FIX ME: refer to better explanation in the paper}
